---
title: "Random_Art"
output: html_document
date: "2023-01-27"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Generating Random Art in R (q 3.2.R2)

### Henrik Godmann

The following function is based on a tutorial about random art in R:
https://art-from-code.netlify.app/day-1/session-1/

It generates pseudo-random data, then randomly chooses one out of 3 
painting styles and one of 150 color palettes and plots the data using ggplot2. 

The code is as follows: 

```{r}


make_art <- function(seed = 87){
  # set seed
  set.seed(seed)
  
  # load required packages 
  library(tibble)
  library(tidyverse)
  library(ggthemes)
  
  # generate random data to visualize 
  set.seed(seed)
  n <- sample(1:100, 1)
  mean <- sample(seq(from = -2, to = 2, by = 0.1), 1)
  sd <- sample(seq(from = 0, to = .99, by = 0.1), 1)
  
  set.seed(seed)
  dat <- tibble(
    x0 = rbeta(n, 1, 3),
    y0 = rbeta(n, 2, 4),
    x1 = x0 + rnorm(n, mean, sd),
    y1 = y0 + rnorm(n, mean, sd),
    shade = runif(n), 
    size = runif(n)
  )
  
  # choose random color palette
  set.seed(seed)
  palette <- canva_palettes[[sample(150,1)]]
  
  # choose random painting style 
  set.seed(seed)
  painting_style <- sample(3, 1)
  
  # plot random data
  # style 1: 
  if (painting_style == 1){
    art <-  dat %>% ggplot(aes(x = x0, y = y0,
                        xend = x1, yend = y1,
                        colour = shade, size = size)) +
      geom_path(show.legend = FALSE) +  
      coord_polar() +
      scale_y_continuous(expand = c(0, 0)) +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_colour_gradientn(colours = palette) +
      scale_size(range = c(0, 10)) + 
      theme_void()
    
  } else if (painting_style == 2) {
    # style 2
    art <- dat %>%
      ggplot(aes(x = x0, y = y0,
                 xend = x1, yend = y1,
                 colour = shade, size = size)) +
      geom_segment(show.legend = FALSE) +  
      coord_polar() +
      scale_y_continuous(expand = c(0, 0)) +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_colour_gradientn(colours = palette) + 
      scale_size(range = c(0, 10)) + 
      theme_void()
    
  } else {
    # style 3
    art <-  dat %>%
      ggplot(aes(x = x0, y = y0,
                 xend = x1, yend = y1,
                 colour = shade, size = size)) +
      geom_point(show.legend = FALSE) +  
      coord_polar() +
      scale_y_continuous(expand = c(0, 0)) +
      scale_x_continuous(expand = c(0, 0)) + 
      scale_colour_gradientn(colours = palette) + 
      scale_size(range = c(0, 10)) + 
      theme_void()
  }
 art

}
```

The function takes the optional argument of a seed to reproduce the same piece of 
art multiple times. The default is 87 which results in the following image: 

```{r}
make_art(17)
```

Here are a few samples from my art collection, drawn by make_art: 

```{r}
make_art(72)
make_art(4)
make_art(94)
make_art(100002)
```


